### 2016-06-13 abstract.tex
abstract: applied polishments to actual (non-commented) english version

Object orientation provides principles for abstraction and encapsulation.
Abstraction is accomplished by high-level concepts of interfaces, classes, and objects.
Many object-oriented languages have followed the blocking and synchronous model of messaging. 
\emph{Asynchronous} message passing is one of the fundamental elements of the actor model.
Unlike in object orientation, a message is not bound to any interface in the actor model.
Ongoing research focuses on combining object-oriented programming with the actor model and concurrency.
In a concurrent setting with objects, multi-threading is a common approach to provide an object-oriented concurrency model.
In contrast, a message in actor model cannot be pre-empted while being processed.
Integration of actor model and object orientation leads to the use of asynchronous method calls.
% Multicore and distributed computing raised a new challenge: combining object orientation, the actor model, and \emph{concurrency}.
Coroutines can be used for collaborative pre-emption.
Coroutines are not originally established in the object-oriented paradigm.
Furthermore, interactions in both coroutines and multi-threading are blocking and synchronous.
The main challenge is to generate production code from an actor-based language which supports asynchronous method calls and coroutine-style execution.

>>>>

Object orientation provides principles for abstraction and encapsulation.
Abstraction is accomplished by high-level concepts of interfaces, classes, and objects.
Many object-oriented languages have followed the blocking and synchronous model of messaging. 
\emph{Asynchronous} message passing is one of the fundamental elements of the actor model.
Unlike in object orientation, a message is not bound to any interface in the actor model.

Ongoing research focuses on combining object-oriented programming with the actor model and concurrency.
In a concurrent setting with objects, multi-threading is a common approach to provide an object-oriented concurrency model.
Integration of actor model and object orientation leads to the use of asynchronous method calls.
However, neither of object-orientation and actor model support explicit control of pre-emption for messages or asynchronous method calls.
%In contrast, a message in actor model cannot be pre-empted while being processed.
In comparison to this rigid ``run to completion''-execution style, coroutines are more flexible: they allow multiple entry points and can be used for collaborative pre-emption between tasks by giving up control with explicit yield or suspend instructions.
Coroutines are not originally established in the object-oriented paradigm.
Furthermore, interactions in both coroutines and multi-threading are blocking and synchronous.
The main challenge is to generate production code from an actor-based language which supports asynchronous method calls and coroutine-style execution.
